\documentclass[a4paper, 11pt, notitlepage]{report}
\begin{document}
\chapter{List of Defenitions}
\begin{description}

  \item[CostDecrease] The write-off of the wheelchairs.
  \item[CostEmployed] The salary of all employees.
  \item[CostEscorts] The total salary of all escorts needed for the modeled transfer.
  \item[CostMaintainers] The total salary of all maintainers involved in the transfer.
  \item[CostMaintenance] The costs of the maintenance of the wheelchairs.
  \item[Costs] The total amount of costs KLM should make for the wheelchair service of the modeled transfer.
  \item [CostWeelchairPerSecond] The costs of a new wheelchair divided by the time it can be used.
  \item[DisabledPeople] The amount of disabled people which need to make the transfer and need to make use of the wheelchair service.
  \item[Distance] The amount of meters from gate of arrival to gate of departure.
  \item[Escorts] The people pushing the wheelchairs.
  \item[Maintainers] The people who maintain the wheelchairs.
  \item[NrDisabled] The amount of disabled people which need to make the transfer and need to make use of the wheelchair service.
  \item[NrEmployed] The amount of employees.
  \item[NrEscorts] The amount of escorts needed for the modeled trasfer.
  \item[NrMaintainers] The amount of maintainers involved in the transfer.
  \item[NrWheelchairs] The amount of wheelchairs needed for the modeled transfer.
  \item[Passengers] The passengers who need a wheelchair and escort to get to a transfer flight.
  \item[Quality] The quality of the wheelchair service.
  \item[Salary] The amount of money a employee gets per hour.
  \item[Speed] The amount of meters a escort can walk in one second.
  \item[TimeBetweenFlights] The time in seconds form arrival to departure of the transfer flight.
  \item[TimeTillDistruction] The amount of time a wheelchair can be used before it needs replacement.
  \item[TotalCostWheelchair] The price of a new wheelchair.
  \item[TotalDistance] The total distance all escorts together should cover to get all disabled to the transfer flight.
  \item[TotalDistance1Escort] The maximum of distance one escort can cover in the time between the arrival and departure of the passenger.
  \item[Vescort] The average speed of a escort.
  \item[WheelchairsPerMaintainer] The amount of wheelchairs one maintainer maintenances.
\end{description}
\end{document} 